\documentclass[12pt]{amsart}
\usepackage{fullpage}

\newcommand{\course}{MATH 2250}
\newcommand{\semester}{Fall 2015}
\newcommand{\instructor}{Danny Krashen}
\newcommand{\website}{http://dkrashen.github.io/calc1/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TYPICAL PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath,amssymb}
\usepackage[all]{xy}
\usepackage{fullpage,enumerate}
\usepackage{url, color, hyperref}

\title{\course, \semester \\ Lecture Schedule}
\author{Instructor: \instructor}

\begin{document}
\maketitle

\begin{enumerate}[1. ]

\item \textbf{Orientation}: introduction to the ideas of calculus, differentiation,
integration, fundamental theorem of calculus. basic ideas of limits and
their relevance. common sense definition of limits (recitation).
\item \textbf{Limits and limit laws} (Mooculus Ch 1): formal definition of
limits, example via definition. limit laws (Mooculus, 1.3), examples.
\item \textbf{Limits, continuity, squeeze}
\begin{enumerate}[ \ \  i. ]
\item
limit laws (1.3) give continuity for polynomials, roots, etc. 
\item
mention that trig functions are continuous (continuity in 2.3).
\item
examples, group work (radical cancellation!).
\item
squeeze (1.3.5), sine (1.3.6)
\item
examples, group work (trig stuff)
\end{enumerate}
\item \textbf{One sided limits, average rates of change, some difference
quotients, derivatives}
\begin{enumerate}[ \ \  i. ]
\item
warm up: practice with trig function limits etc.
\item
definition of one sided limits. comparison with limits.
\item
one-sided limit laws. examples.
\item
infinite limits and asymptotes (2.1).
\item
average rate of change, examples, group work.
\item
difference quotients, derivatives
\item
examples, group work.
\end{enumerate}

\end{enumerate}

\end{document}
