\documentclass[12pt]{amsart}

\newcommand{\course}{MATH 2250}
\newcommand{\semester}{Fall 2015}
\newcommand{\instructor}{Danny Krashen}
\newcommand{\schedule}{
Lectures (15624): TuTh 9:30am-10:45pm, Poultry Sciences 238 \\
Recitation (15624): M 12:20am-1:10am, Aderhold Hall 116 \\
Lectures (25507): TuTh 12:30am-1:45pm, Physics Building 327 \\
Recitation (25507): M 10:10am-11:00am, Physics Building 327
}
\newcommand{\officehour}{Office Hour: TBA}
\newcommand{\phone}{706-542-2555}
\newcommand{\emailaddr}{dkrashen@uga.edu} 
\newcommand{\textbook}{{The Mooculus Textbook}
(\url{https://mooculus.osu.edu/handouts})}
\newcommand{\website}{http://dkrashen.github.io/calc1/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TYPICAL PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath,amssymb}
\usepackage[all]{xy}
\usepackage{fullpage,enumerate}
\usepackage{url, color, hyperref}

\title{\course, \semester}
\author{Instructor: \instructor}

\begin{document}
\maketitle


\thispagestyle{empty}
\noindent
\textsc{Basic Course Information}

\begin{itemize}
\item
\schedule
\item 
\officehour
\item
Office Phone: \phone
\item
Email: \url{\emailaddr}
\item
Textbook: \textbook
\end{itemize}

\medskip

\noindent
\textsc{Online Resources}

\begin{itemize}
\item
Course Webpage:  
\url{\website} 
\end{itemize}

\medskip

\noindent
\textsc{Course Objectives/Topics}

\begin{itemize}
\item
The concept of the derivative.
\item
Derivatives of algebraic, exponential, logarithmic and trigonometric
functions.
\item
Model and solve optimization problems (minimization and
maximization).
\item
Calculate approximate values of functions, sketch graphs.
\item
The concept of the definite integral.
\item
Antiderivates and the evaluation of integrals. Substitution. 
\item
The fundamental theorem of calculus.
\end{itemize}

\medskip

\noindent
\textsc{Grading Policy}

\begin{itemize}
\item
3 Mid-semester exams worth 20\% each (Sep 14, Oct 12, Nov 16)
\item
Homework worth 15\% (lowest 2 scores are dropped), 
\item
Final exam worth 25\%.
\end{itemize}

\medskip

\noindent
\textsc{Academic Honesty}

As a University of Georgia student, you have agreed to abide by the
University’s academic honesty policy, ``A Culture of Honesty,'' and the
Student Honor Code.  All academic work must meet the standards described in
``A Culture of Honesty'' found at: 
\\ \url{http://www.uga.edu/honesty}.  
\\
Lack
of knowledge of the academic honesty policy is not a reasonable explanation
for a violation.  Questions related to course assignments and the academic
honesty policy should be directed to the instructor.



\smallskip

\textit{The course syllabus is a general plan for the course; deviations
announced to the class by the instructor may be necessary.}


\end{document}
